---
title: "Plots for resolution paper"
author: "Richard D. Morey"
date: "25 August 2016"
output: pdf_document
---

Some of this code was adapted from https://github.com/jtleek/replication_paper (in particular, the data loading.)

```{r echo=FALSE,message=FALSE,warning=FALSE}

knitr::opts_chunk$set(fig.path='figs/',echo=FALSE, warning=FALSE, message=FALSE)

options(digits = 2)
library(xtable)
set.seed(1234)

source('loadData.R',chdir=TRUE)
source('plot_funcs.R',chdir=TRUE)

par.list = list(las = 1,
    yaxs="i",mgp = c(2.5,.5,0), tcl = -0.25)
```

```{r}
all.idx = c(5, 29, 60, 66, 68)
all.idx.in.dat = match(pi_dat_nona[all.idx,"ID"],dat$ID)

```

How many total studies are we left with after cleaning?
```{r echo=FALSE}
nrow(pi_dat_nona)
```

```{r zexp,echo=FALSE,fig.width=4,fig.height=8}
do.call(par,par.list)
#par(par.list)

par(mfrow=c(2,1),mar=c(4,4.5,1.2,0))
rr = seq(-.999,.999,len=500)

plot(rr,atanh(rr),ty='l',lwd=2,ylab="Fisher's z",
     xlab="Correlation",ylim=c(-3,3),xlim=c(-1,1))
abline(v=c(-1,1),col=rgb(0,0,0,.3))

mtext("A",3,.1,adj=.95,cex=1.5)


rr = seq(-.99,.99,len=50)

zz = outer(rr,rr,function(a,b){atanh(b)-atanh(a)})
qq = c(.1,.3,.5,.7,1,1.5,3)
qq0 = c(-rev(qq),qq)
contour(rr,rr,zz,levels=qq0,drawlabels=FALSE,
        lwd=2,yaxs="i",xaxs="i",xlab="Correlation, original",
        ylab="Correlation, replication",las=1)
abline(0,1,col="gray")
abline(h=seq(-.9,.9,.1),col=rgb(0,0,0,.1))
abline(v=seq(-.9,.9,.1),col=rgb(0,0,0,.1))
for(i in 1:length(qq0)){
  s = uniroot(function(a,d){
    atanh(a)-atanh(-a) - d
  },c(-1,1),d=qq0[i])$root
  TeachingDemos::shadowtext(s-.02,-s+.02,qq0[i],col="black", bg="white",srt=45)
}

mtext("Diff. in z units",3,.1,adj=.05,cex=1.2)

mtext("B",3,.1,adj=.95,cex=1.5)



```

```{r powtab,echo=FALSE,fig.width=6,fig.height=10}

old.mar = par()$mar
par(mar=c(1,6,6,1))
par(mfrow=c(2,1))

plot(0,0,xlim=c(-1,1),ylim=c(-1,1),axes=FALSE,ylab="",xlab="",ty='n')
box(lwd=3)
rect(0,0,2,2,density = 10,col="lightgray",border=NA)
rect(0,0,-2,-2,density = 10,col="lightgray",border=NA)

abline(v=0,lwd=3)
abline(h=0,lwd=3)

mtext("State of nature",2,4,cex=2)
mtext("Decision",3,4,cex=2)

mtext(expression(paste(H[0]," true")),2,adj=.85,cex=1.5)
mtext(expression(paste(H[0]," false")),2,adj=.15,cex=1.5)

mtext(expression(paste("Reject ", H[0])),3,adj=.85,cex=1.5)
mtext(expression(paste("Don't reject ",H[0])),3,adj=.15,cex=1.5)

rect(0,0,2,2,density = 10,col="lightgray",border=NA)

text(.5,.6,"Type I error",cex=1.5)
text(.5,.4,expression(alpha),cex=1.5)

text(-.5,.6,"Correct decision",cex=1.5)
text(-.5,.4,expression(1-alpha),cex=1.5)


text(-.5,-.4,"Type II error",cex=1.5)
text(-.5,-.6,expression(beta),cex=1.5)

text(.5,-.4,"Correct decision",cex=1.5)
text(.5,-.6,expression(1-beta),cex=1.5)
text(.5,-.8,"Power",cex=1.5)


par(mar=old.mar)
do.call(par,par.list)

zz = seq(-2,2,len=100)
alpha=0.05
N=c(10,50)

plot(tanh(zz),
     pnorm(qnorm(alpha/2,0,1/sqrt(N[1]-3)),zz,1/sqrt(N[1]-3))+
     1-pnorm(qnorm(1-alpha/2,0,1/sqrt(N[1]-3)),zz,1/sqrt(N[1]-3)),ty='l',ylab=expression(paste("power(",rho,")")),ylim=c(0,1),lwd=2,xlab=expression(paste("Correlation ",rho)),xlim=c(-1,1))
abline(h=alpha,col="gray",lwd=1,lty=2)
abline(h=.8,col="gray",lwd=1,lty=2)

text(par()$usr[1],alpha,expression(paste("Type I error rate ",alpha)),adj=c(0,-.2),cex=1.3,col="gray")

lines(tanh(zz),
     pnorm(qnorm(alpha/2,0,1/sqrt(N[2]-3)),zz,1/sqrt(N[2]-3))+
     1-pnorm(qnorm(1-alpha/2,0,1/sqrt(N[2]-3)),zz,1/sqrt(N[2]-3)),lwd=2,lty=3)

points(0,alpha,pch=21,cex=1.3,col="black",bg="white")

text(-.8,.4,substitute(N==N1,list(N1=N[1])))
text(.25,.9,substitute(N==N2,list(N2=N[2])))

```
  
  
```{r echo=FALSE} 

get.other.z=Vectorize(function(z,pow1=.8,pow2=.5,alpha=0.05,maxN=1000){
  get.pow.N = function(N,z,pow1,alpha){
    crits = qnorm(c(alpha/2,1-alpha/2),0,1/sqrt(N-3))
    (diff(pnorm(crits,z,1/sqrt(N-3))) - (1-pow1))^2
  }
  get.pow.z = function(z,N,pow1,alpha){
    get.pow.N(N,z,pow1,alpha)
  }

  Ns = 5:maxN
  devs = sapply(Ns,get.pow.N,z=z,pow1=pow1,alpha=alpha)
  reqN = Ns[which.min(devs)]
  if(get.pow.N(reqN,z=z,pow1=pow1,alpha=alpha)<pow1){
    reqN = reqN + 1
  }
  z2= optimize(get.pow.z,c(0,2*z),N=reqN,pow1=pow2,alpha=alpha)$minimum
  c(N=reqN,z=z2,alpha=alpha)
},"z")

```


```{r powfail,echo=FALSE,fig.width=6,fig.height=6.5}


do.call(par,par.list)

alpha = 0.05

ex.row = 70
n = pi_dat_nona[ex.row,"n_orig"]

n2 = pi_dat_nona[ex.row,"n_rep"]

crit.z = qnorm(c(alpha/2,1-alpha/2), 0,1/sqrt(n-3))
true.z1 = .3962035
true.z2 = 0.277165

y.expand = 1.1
alpha = 0.05

par(mfrow=c(2,1))

zz = seq(-1,1,len=200)
yy = dnorm(zz,0,1/sqrt(n-3))
yy2 = dnorm(zz,true.z1,1/sqrt(n-3))
yy3 = dnorm(zz,true.z2,1/sqrt(n-3))

plot(zz, yy, ty='l', ylab="Density", xlab="Fisher's z",axes=FALSE,ylim=c(0,y.expand*max(yy)),lwd=2,lty=2)
box()
axis(1)
axis(3, at = seq(-1,1,.5), lab=round(tanh(seq(-1,1,.5)),2))
mtext("Correlation, r",3,2.5,adj=.5)

lines(zz,yy2,lwd=2,lty=1)
lines(zz,yy3,lwd=2,lty=1)

abline(v=crit.z,col="gray")
xx = seq(crit.z[2],max(zz),len=100)
yy2 = dnorm(xx,true.z1,1/sqrt(n-3))
yy3 = dnorm(xx,true.z2,1/sqrt(n-3))
polygon(c(xx,rev(xx)),c(yy2,yy2*0),col=rgb(1,0,0,.3))
polygon(c(xx,rev(xx)),c(yy3,yy3*0),col=rgb(0,0,1,.3))

mtext("A",3,-2,adj=.05,cex=1.5)


dd = seq(.1,1,len=100)
z = get.other.z(z = dd)

plot(tanh(dd),tanh(z["z",]),ty='l',xlab=expression(paste("If you power 80% to this ",rho,"...")),ylab=expression(paste("..you're likely to miss ",rho,"s less than")),lwd=2)

abline(h=seq(.1,1,.1),col=rgb(0,0,0,.1))
abline(v=seq(.1,1,.1),col=rgb(0,0,0,.1))

mtext("B",3,-2,adj=.05,cex=1.5)


```

```{r powexp,echo=FALSE,fig.width=6,fig.height=6.5}

#example
ex.row = 70

do.call(par,par.list)

n = pi_dat_nona[ex.row,"n_orig"]
r = -pi_dat_nona[ex.row,"cor_orig"]
z = atanh(r)

n2 = pi_dat_nona[ex.row,"n_rep"]

true.cor = .1
true.z = atanh(true.cor)

y.expand = 1.1
alpha = 0.05

par(mfrow=c(2,1))

zz = seq(-1,1,len=200)
yy = dnorm(zz,true.z,1/sqrt(n-3))
plot(zz, yy, ty='l', ylab="Density", xlab="Fisher's z",axes=FALSE,ylim=c(0,y.expand*max(yy)),lwd=2)
box()
axis(1)
axis(3, at = seq(-1,1,.5), lab=round(tanh(seq(-1,1,.5)),2))
mtext("Correlation, r",3,2.5,adj=.5)
mtext(substitute(rho==tc,list(tc=true.cor)),3,-1.5,adj=.95, cex=1.3)

crit = qnorm(alpha, true.z,1/sqrt(n-3))
abline(v=crit,col="gray")
xx = seq(min(zz),crit,len=100)
yy2 = dnorm(xx,true.z,1/sqrt(n-3))
polygon(c(xx,rev(xx)),c(yy2,yy2*0),col=rgb(1,0,0,.3))
text(crit,par()$usr[4],substitute(alpha==alp,list(alp=alpha)),
     srt=90,adj=c(1.1,1.2),col="gray")
text(crit,par()$usr[4],substitute(r==r0,list(r0=round(tanh(crit),2))),
     srt=90,adj=c(1.1,-.2),col="gray")

abline(v=z,col="gray")
xx = seq(min(zz),z,len=100)
yy2 = dnorm(xx,true.z,1/sqrt(n-3))
polygon(c(xx,rev(xx)),c(yy2,yy2*0),col=rgb(0,0,1,.3))
text(z,par()$usr[4],"Observed r",srt=90,adj=c(1.1,-.1),col="gray")

true.cor2 = -.1
true.z2 = atanh(true.cor2)
yy = dnorm(zz,true.z2,1/sqrt(n-3))
plot(zz, yy, ty='l', ylab="Density", xlab="Fisher's z",axes=FALSE,ylim=c(0,y.expand*max(yy)),lwd=2)
box()
axis(1)
axis(3, at = seq(-1,1,.5), lab=round(tanh(seq(-1,1,.5)),2))
mtext("Correlation, r",3,2.5,adj=.5)
mtext(substitute(rho==tc,list(tc=true.cor2)),3,-1.5,adj=.95, cex=1.3)

crit = qnorm(alpha, true.z,1/sqrt(n-3))
abline(v=crit,col="gray")
xx = seq(min(zz),crit,len=100)
yy2 = dnorm(xx,true.z2,1/sqrt(n-3))
polygon(c(xx,rev(xx)),c(yy2,yy2*0),col=rgb(1,0,0,.3))
text(crit,par()$usr[4],substitute(alpha==alp,list(alp=alpha)),
     srt=90,adj=c(1.5,1.2),col="gray")
```


```{r powexp2,echo=FALSE,fig.width=6,fig.height=6.5}

do.call(par,par.list)

par(mfrow=c(2,1))

zz = seq(-1,1,len=200)
yy = pnorm(crit,zz,1/sqrt(n-3))
plot(zz, yy, ylab="Power", xlab="True Fisher's z",axes=FALSE,ylim=c(0,y.expand*max(yy)),lwd=2,ty='n')
zz = seq(-1.2,true.z,len=200)
yy = pnorm(crit,zz,1/sqrt(n-3))
lines(zz, yy,lwd=2)
abline(v = true.z, col="gray")
text(true.z,par()$usr[4],substitute(rho==rh,list(rh=true.cor)),
     srt=90,adj=c(1.5,1.2),col="gray")

box()
axis(1)
axis(2,at=0:4/4)
axis(3, at = seq(-1,1,.5), lab=round(tanh(seq(-1,1,.5)),2))
mtext(expression(paste("True correlation, ",rho)),3,2.5,adj=.5)
mtext(substitute(rho>=tc,list(tc=true.cor)),3,-1.5,adj=.95, cex=1.3)

segments(true.z2,0,true.z2,pnorm(crit,true.z2,1/sqrt(n-3)),col="red")
segments(true.z2,pnorm(crit,true.z2,1/sqrt(n-3)),-1.2,pnorm(crit,true.z2,1/sqrt(n-3)),col="red")


crit2 = qnorm(alpha, 0,1/sqrt(n2-3))

zz = seq(-1,1,len=200)
yy = pnorm(crit2,zz,1/sqrt(n2-3))
plot(zz, yy, ylab="Power", xlab="True Fisher's z",axes=FALSE,ylim=c(0,y.expand*max(yy)),lwd=2,ty='n')
zz = seq(-1.2,0,len=200)
yy = pnorm(crit2,zz,1/sqrt(n2-3))
lines(zz, yy,lwd=2)
abline(v = 0, col="gray")
text(0,par()$usr[4],expression(rho==0),
     srt=90,adj=c(1.5,1.2),col="gray")

rect(zz[which.min((yy - .5)^2)],0,0,2,col=rgb(0,0,0,.3),density=10)

box()
axis(1)
axis(2,at=0:4/4)
axis(3, at = seq(-1,1,.5), lab=round(tanh(seq(-1,1,.5)),2))
mtext(expression(paste("True correlation, ",rho)),3,2.5,adj=.5)
mtext(expression(rho>=0),3,-1.5, adj=.95, cex=1.3)

segments(z,0,z,pnorm(crit2,z,1/sqrt(n2-3)),col="red")
segments(z,pnorm(crit2,z,1/sqrt(n2-3)),-1.2,pnorm(crit2,z,1/sqrt(n2-3)),col="red")

```

Power on top graph
```{r}
pnorm(crit,true.z2,1/sqrt(n-3))
```
Power on bottom graph
```{r}
pnorm(crit2,z,1/sqrt(n2-3))
```

Value with 50% power
```{r}
zz[which.min((yy - .5)^2)]
```

$p$ value for observation
```{r}
pnorm(z,true.z,1/sqrt(n-3))
```

----

```{r}
# Their result
shuf = pi_dat_nona
ccs = seq(.5,.99,len=100)
ip = sapply(ccs,function(cc){
  z = data.frame(t(apply(shuf,1,do.one,cc=cc)))
  mean(!z$too_low & !z$too_high)
})
ip = data.frame("Inc.Prop" = ip)
rownames(ip) = paste0(ccs * 100,"%")
ip$Prop.of.Exp = ip[,1] / ccs
```

What proportion of the replications are in the prediction CI when we permute the results?
```{r}
# Randomize original results
s = replicate(10000,{
  shuf = pi_dat_nona
  shuf$cor_orig = sample(shuf$cor_orig)
  z = data.frame(t(apply(shuf,1,do.one)))
  mean(!z$too_low & !z$too_high)
})
sr.rand = mean(s)

sr.rand
```


What proportion of replications are in the prediction CI when we set all the original results to 0 effect size?
```{r}
# All original results 0
shuf = pi_dat_nona
shuf$cor_orig = shuf$cor_orig*0
z = data.frame(t(apply(shuf,1,do.one)))
sr.all0 = mean(!z$too_low & !z$too_high)

sr.all0
```


What proportion of replications are in the prediction CI when we set all the original results to the same effect size of the replications, but with opposite sign?
```{r}
# original results opposite sign of replications
shuf = pi_dat_nona
shuf$cor_orig = -shuf$cor_rep
z = data.frame(t(apply(shuf,1,do.one)))
sr.oppsign = mean(!z$too_low & !z$too_high)

sr.oppsign
```

```{r}
Ns = dat[all.idx.in.dat,c("N..O.","N..R.")]
cors = pi_dat_nona[all.idx,c("cor_orig","cor_rep","se_total")]
spec_tab = cbind(Ns,cors[,1:2],atanh(cors[,1])-atanh(cors[,2]),cors[,3])
rownames(spec_tab) = letters[1:nrow(spec_tab)]
colnames(spec_tab) = c("Orig. N","Repl. N","Orig. r", "Repl. r","Observed difference (Fisher's z)","SE of difference (Fisher's z)")



## ----special_table,echo=FALSE,results='asis'-----------------------------
knitr::kable(spec_tab)
```

```{r echo=FALSE}
in.95 = mean(!(pi_dat_nona$too_high | pi_dat_nona$too_low))
in.se = mean(abs((atanh(pi_dat_nona$cor_orig) -  
          atanh(pi_dat_nona$cor_rep))) < pi_dat_nona$se_total)
in.99 = mean(abs((atanh(pi_dat_nona$cor_orig) -  
          atanh(pi_dat_nona$cor_rep))) < qnorm(1-.01/2)*pi_dat_nona$se_total)

in.50 = mean(abs((atanh(pi_dat_nona$cor_orig) -  
          atanh(pi_dat_nona$cor_rep))) < qnorm(1-.5/2)*pi_dat_nona$se_total)

```

How many 95% prediction intervals contain replication?
```{r}
in.95*nrow(pi_dat_nona)
```

How many 99% prediction intervals contain replication?

```{r}
in.99*nrow(pi_dat_nona)
```

How many 50% prediction intervals contain replication?

```{r}
in.50*nrow(pi_dat_nona)
```

How many prediction SE intervals contain replication?
```{r}
in.se*nrow(pi_dat_nona)
```


```{r conf.coef,echo=FALSE,fig.width=6,fig.height=4}


do.call(par,par.list)
plot(ccs,ip[,1],ylab="Proportion included in pred. CI",xlab="Confidence Coefficient",ty='l',lwd=2,axes=FALSE,ylim=c(0,1))
axis(2)
segments(.95,in.95,par()$usr[1],in.95,col=rgb(0,0,0,.3),lty=2)
segments(.95,in.95,.95,par()$usr[3],col=rgb(0,0,0,.3),lty=2)
text(par()$usr[1],in.95,adj=c(-.1,-.1),"95% prediction CI")
segments(1-2*pnorm(-1),in.se,par()$usr[1],in.se,col=rgb(0,0,0,.3),lty=2)
segments(1-2*pnorm(-1),in.se,1-2*pnorm(-1),par()$usr[3],col=rgb(0,0,0,.3),lty=2)
text(par()$usr[1],in.se,adj=c(-.1,-.1),"±1 pred. SE")

axis(1, at = seq(.5,1,.1),lab=paste0(100*seq(.5,1,.1),"%"))
abline(0,1,lty=3,col=rgb(1,0,0,.3))
```

```{r resid1,echo=FALSE,fig.width=6,fig.height=4}

cx = sqrt(pi_dat_nona$n_orig / min(pi_dat_nona$n_orig)*.5)

do.call(par,par.list)
par(mfrow=c(1,1),mar=c(4,4,3.7,4))
plot(atanh(pi_dat_nona$cor_orig),atanh(pi_dat_nona$cor_orig) - atanh(pi_dat_nona$cor_rep),
     ylim=c(-1.4,1.4),ylab=c("Observed diff. (Fisher's z)"),xlab="Original study's correlation",
     pch=21,col=NA,bg=rgb(!nsig,0,0,.3),cex=cx,axes=FALSE,
     xlim=c(-.1,atanh(.9)))
axis(2)
axis(1, at = atanh(seq(0,.8,.2)),lab=seq(0,.8,.2))
axis(3, at = seq(0,1.25,.25))
mtext("Original study's Fisher's z",3,2.5,adj=.5)
box()

segments(atanh(pi_dat_nona$cor_orig),
         atanh(pi_dat_nona$cor_orig) - atanh(pi_dat_nona$cor_rep) + pi_dat_nona$se_total,
         atanh(pi_dat_nona$cor_orig),
         atanh(pi_dat_nona$cor_orig) - atanh(pi_dat_nona$cor_rep) - pi_dat_nona$se_total,
         rgb(!nsig,0,0,.4))
abline(h=0,col=rgb(0,0,0,.3),lty=2)
abline(v=0,col=rgb(0,0,0,.3),lty=2)
abline(0,1,lty=3,col=rgb(0,0,1,.3))

axis(4,at=seq(-1,1,.5),lab=round(tanh(seq(-1,1,.5)),2),cex.axis=1)
mtext(expression(paste("Difference (correlation, original ",r==0,")")),4,2.9,adj=.5,las=3)
mtext("Orig. > Repl.",3,-1.5,cex=1.3,adj=.05)
mtext("Repl. > Orig.",1,-1.5,cex=1.3,adj=.05)

for(i in 1:nrow(spec_tab)){
  text(atanh(spec_tab$`Orig. r`[i]), spec_tab$`Observed difference (Fisher's z)`[i],letters[i],adj=c(1,1),cex=1.3)
}
```



What is the median $z$ score?
```{r echo=FALSE}
median(z.score)
```

```{r power1,echo=FALSE,fig.width=6,fig.height=8}

do.call(par,par.list)
par(mfrow=c(2,1))

plot(ecdf(z.score),main="",axes=FALSE,xlab="z score of difference",ylab="Proportion less than")
axis(2,at = seq(0,1,len=6), las=1)
axis(1)
pp = round(c(2*pnorm(-1), .1, .05, .01, .001),3)
axis(3, at = -qnorm(pp/2),pp,cex.axis=.75,las=3)
axis(3, at = qnorm(pp/2),pp,cex.axis=.75,las=3)
box()
abline(h=c(1:4/5),col=rgb(0,0,0,.3))
rect(par()$usr[1],par()$usr[3],par()$usr[2],par()$usr[4],col=rgb(1,0,0,.1),border=NA)
for(i in 1:length(pp))
rect(-qnorm(pp[i]/2),par()$usr[3],qnorm(pp[i]/2),par()$usr[4],col=rgb(0,0,1,.1),border=NA)
xx = seq(-6,7,len=100)
lines(xx,pnorm(xx),col="red",lty=2,lwd=1)
mtext("Two-tailed p value", 3, 3, adj=.5)

alpha = 0.05
dev = seq(0,2.5,len=100)
pows = sapply(1:nrow(pi_dat_nona),function(i){
  pow = (1-pnorm(-qnorm(alpha/2),dev/pi_dat_nona$se_total[i])) + 
    pnorm(qnorm(alpha/2),dev/pi_dat_nona$se_total[i])
})
matplot(dev,pows,ty='l',ylim=c(0,1),las=1,ylab=
          substitute(paste("Power (",alpha == alp, ")", sep="" ),list(alp = alpha)),
        xlab="True difference (Fisher's z)",col=rgb(0,0,0,.2),lwd=1,lty=1)
abline(h=.8,col="black",lty=2)
axis(3,at=seq(0,2.5,.33),lab=round(tanh(seq(0,2.5,.33)),2))
mtext(expression(paste("True difference (correlation, original ",rho==0,")")),3,2.5,adj=.5)
lines(dev,apply(pows,1,median),lwd=3,col="red",lty=1)
lines(dev,apply(pows,1,quantile,p=.25),lwd=3,col="blue",lty=1)
lines(dev,apply(pows,1,quantile,p=.75),lwd=3,col="blue",lty=1)

```

What are the quartiles of the power at a difference of .3?
```{r echo=FALSE}
quantile(sapply(1:nrow(pi_dat_nona),function(i){
  pow = (1-pnorm(-qnorm(alpha/2),.3/pi_dat_nona$se_total[i])) + 
    pnorm(qnorm(alpha/2),.3/pi_dat_nona$se_total[i])
}), p = c(.25,.5,.75))

```


```{r echo=FALSE}
dev = .3
p.null = round(1-pchisq(z.score[all.idx]^2,1),3)
p.sev = round(pchisq(z.score[all.idx]^2,1,(dev/pi_dat_nona$se_total[all.idx])^2),3)

dd = seq(0,2.5,len=100)
pp = sapply(dd,function(dev){
  pchisq(z.score^2,1,ncp = (dev/pi_dat_nona$se_total)^2)
})
```


These are the p values against the null.
```{r}
p.null
```

These are the p values against $d\geq.3$.
```{r}
p.sev
```



```{r severity1,echo=FALSE,fig.width=6,fig.height=6.5}

do.call(par,par.list)
par(mfrow=c(2,2),mar = c(4.5,4,4.5,2))
dev = .3
idx = all.idx[1]

make.pvalue.plot(pi_dat_nona$cor_orig[idx],
                 pi_dat_nona$n_orig[idx],
                 pi_dat_nona$cor_rep[idx],
                 pi_dat_nona$n_rep[idx],
                 true.d = dev,
                 xlims = c(-1,1.5),
                 par.list = par.list,
                 TRUE,
                 TRUE)

mtext("Study a",3,-1.3,adj=.95,cex=1)


make.pvalue.curve.plot(pi_dat_nona$cor_orig[idx],
                 pi_dat_nona$n_orig[idx],
                 pi_dat_nona$cor_rep[idx],
                 pi_dat_nona$n_rep[idx], true.d=.3, xmax=2.5, par.list = par.list)


mtext("Study a",3,-1.3,adj=.95,cex=1)


idx = all.idx[2]

make.pvalue.plot(pi_dat_nona$cor_orig[idx],
                 pi_dat_nona$n_orig[idx],
                 pi_dat_nona$cor_rep[idx],
                 pi_dat_nona$n_rep[idx],
                 true.d = dev,
                 xlims = c(-1,1.5),
                 par.list = par.list,
                 TRUE,
                 TRUE)

mtext("Study b",3,-1.3,adj=.95,cex=1)


make.pvalue.curve.plot(pi_dat_nona$cor_orig[idx],
                 pi_dat_nona$n_orig[idx],
                 pi_dat_nona$cor_rep[idx],
                 pi_dat_nona$n_rep[idx], true.d=.3, xmax=2.5, par.list = par.list)


mtext("Study b",3,-1.3,adj=.95,cex=1)


```

```{r severity2,echo=FALSE,fig.width=6,fig.height=8}



do.call(par,par.list)
par(mfrow=c(2,1))
matplot(dd,t(pp),ty='l',ylim=c(0,1),ylab=expression(paste(p[phantom()>phantom()], " value ")),xlab="True difference (abs. value of Fisher's z)",col=rgb((z.score^2>qchisq(.95,1)),0,0,.3),lwd=1,lty=(z.score^2>qchisq(.95,1))+1)
axis(3,at=seq(0,2.5,.33),lab=round(tanh(seq(0,2.5,.33)),2),cex.axis=.75)
mtext(expression(paste("True difference (correlation, original ",rho==0, ")")),3,2.5,adj=.5)
matlines(dd,t(pp[all.idx[3:5],]),lwd=2,lty=(z.score[all.idx[3:5]]^2>qchisq(.95,1))+1,col=rgb((z.score[all.idx[3:5]]^2>qchisq(.95,1)),0,0,1))

text(.05,.35,"c",cex=1.3)
text(.95,.4,"d",cex=1.3)
text(2,.2,"e",cex=1.3)

plot(dd, colMeans(pp[(z.score^2<qchisq(.95,1)),]<0.05),col=rgb(0,0,0,1),ty='l',lwd=2,ylab=expression(paste("Proportion ",p[phantom()>phantom()]<0.05)),xlab="True difference (abs. value of Fisher's z)",ylim=c(0,1))
abline(h=c(0,1),col=rgb(0,0,0,.5))
abline(v=0,col=rgb(0,0,0,.5))

axis(3,at=seq(0,2.5,.33),lab=round(tanh(seq(0,2.5,.33)),2),cex.axis=.75)
mtext(expression(paste("True difference (correlation, original ",rho==0,")")),3,2.5,adj=.5)

sev3 = mean(pchisq(z.score^2,1,ncp = (.3/pi_dat_nona$se_total)^2)[(z.score^2<qchisq(.95,1))]<.05)

segments(.3,sev3,par()$usr[1],sev3,lty=2,col="gray")
segments(.3,sev3,.3,par()$usr[3],lty=2,col="gray")
axis(1, at = .3)

```

```{r reppower1,echo=FALSE,fig.width=6,fig.height=4}


dev = seq(0,2.2,len=100)
N = seq(10,2000,50)
pp = outer(dev,N,function(dev,N2,N1,alpha=0.05){
  1-pchisq(qchisq(1-alpha,1),1,dev^2/(1/(N1-3)+1/(N2-3)))
},N1=9)

filled.contour(dev,log(N),pp,ylab="Sample size",xlab="True difference (Fisher's z)",
               plot.axes = {
                 N.at = round(exp(seq(log(min(N)),log(max(N)),len=5)))
                 axis(2,at=log(N.at),lab=N.at)
                 axis(1)
                 axis(3,at=seq(0,2.5,.33),lab=round(tanh(seq(0,2.5,.33)),2))
                 mtext(expression(paste("True difference (correlation, original ", rho==0,")")),3,2.5,adj=.5)
                 contour(dev, log(N), pp, levels = c(1:4/5,.95), 
                         drawlabels = TRUE, axes = FALSE, 
                         frame.plot = FALSE, add = TRUE,labcex = 1)
                 abline(v=.3,col="gray",lty=2)
                 text(.3,log(100),"True difference = 0.3",srt=90,col="gray",adj=c(.5,-.1))
               },
               key.title = title(main = "Power"),xlim=c(0,2))
```


```{r reppower2,echo=FALSE,fig.width=6,fig.height=4}
do.call(par,par.list)

#dev = seq(0,2.7,len=100)

pow.lim = outer(dev,Inf,function(dev,N2,N1,alpha=0.05){
  1-pchisq(qchisq(1-alpha,1),1,dev^2/(1/(N1-3)+1/(N2-3)))
},N1=9)

pow3 = 1-pchisq(qchisq(0.95,1),1,.3^2/(1/(9-3)+1/(Inf-3)))

plot(dev,pow.lim,lwd=2,ty='l',xlab="True difference (Fisher's z)",ylab=expression(paste("Power limit (",N[rep]==infinity,")")),xlim=c(0,2),ylim=c(0,1),cex.lab=1)
#mtext(expression(paste(N[orig]==9)),3,.1,adj=1,cex=1.3)
abline(h=.8,col="black",lty=2)
abline(h=c(0,1),col="gray",lty=1)
abline(v=0,col="gray")
segments(.3,pow3,par()$usr[1],pow3,lty=2,col="gray")
segments(.3,pow3,.3,par()$usr[3],lty=2,col="gray")
axis(3,at=seq(0,2,.33),lab=round(tanh(seq(0,2,.33)),2),cex.axis=.75)
mtext(expression(paste("True difference (correlation, original ", rho==0,")")),3,2.5,adj=.5)

axis(1,at=.3)
axis(2,at=pow3,lab=round(pow3,2))
```


```{r reppower3,echo=FALSE,fig.width=6,fig.height=4}

dev = seq(0,1,len=100)
N = seq(50,2000,50)
pp = outer(dev,N,function(dev,N,alpha=0.05){
  1-pchisq(qchisq(1-alpha,1),1,dev^2/2 * (N-3))
})

filled.contour(dev,log(N),pp,ylab="Sample size",xlab="True difference (Fisher's z)",
               plot.axes = {
                 N.at = round(exp(seq(log(min(N)),log(max(N)),len=5)))
                 axis(2,at=log(N.at),lab=N.at)
                 axis(1)
                 axis(3,at=seq(0,2.5,.33),lab=round(tanh(seq(0,2.5,.33)),2))
                 mtext(expression(paste("True difference (correlation, original ",rho==0,")")),3,2.5,adj=.5)
                 contour(dev, log(N), pp, levels = c(1:4/5,.95), 
                         drawlabels = TRUE, axes = FALSE, 
                         frame.plot = FALSE, add = TRUE,labcex = 1)
               },
               key.title = title(main = "Power"))


```

